$\pi$ with leftovers: \\ a mechanisation in Agda

### 2020-09-22 paper/paper.tex
Anon supress previous work

The authors would also like to thank the anonymous referees fortheir valuable comments and helpful suggestions. This work is supported by the \grantsponsor{UKEPSRC}{UK EPSRC}{} grant \grantnum{UKEPSRC}{EP/K034413/1} ``From Data Types to Session Types: A Basis for Concurrency and Distribution'' (ABCD), and by the \grantsponsor{EUHORIZON}{EU HORIZON 2020 MSCA RISE}{} project \grantnum{EUHORIZON}{778233} ``Behavioural Application Program Interfaces'' (BehAPI).
\end{acks}

@@

In her master's thesis, Zalakain uses a HOAS to embed a session-typed \picalc{} in Coq \cite{Zalakain2019}.
Channel type polymorphism (preventing channels from being constructed out of thin air) and a process-traversing predicate ensure that channels are used linearly --- subject reduction is then shown to preserve this predicate.

>>>>

The authors would also like to thank the anonymous referees for their valuable comments and helpful suggestions. This work is supported by the \grantsponsor{UKEPSRC}{UK EPSRC}{} grant \grantnum{UKEPSRC}{EP/K034413/1} ``From Data Types to Session Types: A Basis for Concurrency and Distribution'' (ABCD), and by the \grantsponsor{EUHORIZON}{EU HORIZON 2020 MSCA RISE}{} project \grantnum{EUHORIZON}{778233} ``Behavioural Application Program Interfaces'' (BehAPI).
\end{acks}

@@

\begin{anonsuppress}
In her master's thesis, Zalakain uses a HOAS to embed a session-typed \picalc{} in Coq \cite{Zalakain2019}.
Channel type polymorphism (preventing channels from being constructed out of thin air) and a process-traversing predicate ensure that channels are used linearly --- subject reduction is then shown to preserve this predicate.
\end{anonsuppress}
